R for Clinical Study Reports and Submission

### 2021-09-13 intro.Rmd
Changes on Intro

In clinical trial development, developers needs to organize source code to deliver Study Data Tabulation Model (SDTM) or Analysis Dataset Model (ADaM) datasets and table, listing and figures (TLFs).
For example, a Phase 3 clinical trial typically require hundreds of TLFs. 
A consistent and well-defined folder structure is crucial to manage a clinical trial analysis and reporting (A&R) project.

@@

- For an organization, it simplify process, tool, template, and training development, because a unified folder structure is used to develop and maintain standard tool and analysis project.

@@

- Part 1, "Delivering TLFs in CSR" provides general information with examples to create table, listing and figures. 
In this part, we assume readers are an individual contributor of a clinical project with some experience in R programming. 
We expect readers are familiar with data manipulation in R. Some good reference includes [Hands-On Programming with R](https://rstudio-education.github.io/hopr/), 
[R for Data Science](https://r4ds.had.co.nz/) and [Data Manipulation with R](https://www.amazon.com/Data-Manipulation-R-Use/dp/0387747303).

@@

- Part 3, "eCTD Submission package" provides general information in preparing 
submission package related to clinical study report (CSR) in 
electronic Common Technical Document (eCTD). 
In this part, we assume a reader is a project lead of a clinical project 
with experience in R package development as well.

>>>>

In clinical trial development, developers needs to organize source code to deliver Study Data Tabulation Model (SDTM) or Analysis Dataset Model (ADaM) datasets and tables, listings and figures (TLFs).
For example, a Phase 3 clinical trial typically require hundreds of TLFs. 
A consistent and well-defined folder structure is crucial to manage a clinical trial analysis and reporting (A&R) project.

@@

- For an organization, it simplifies process, tool, template, and training development, because a unified folder structure is used to develop and maintain standard tool and analysis project.

@@

- Part 1, "Delivering TLFs in CSR" provides general information with examples to create tables, listings and figures. 
In this part, we assume readers are individual contributors of a clinical project with some experience in R programming. 
We expect readers are familiar with data manipulation in R. Some good reference includes [Hands-On Programming with R](https://rstudio-education.github.io/hopr/), 
[R for Data Science](https://r4ds.had.co.nz/) and [Data Manipulation with R](https://www.amazon.com/Data-Manipulation-R-Use/dp/0387747303).

@@

- Part 3, "eCTD Submission package" (maybe provide the full spelling for "eCTD" here) provides general information in preparing 
submission package related to clinical study report (CSR) in 
electronic Common Technical Document (eCTD). 
In this part, we assume a reader is a project lead of a clinical project 
with experience in R package development as well.
